The value of intermediation

### 2022-11-17 src/presentation/micro_seminar_talk.qmd
Change investment cost notation (c -> i)

 - Intentionally simple model
 - Most elements borrowed from [@anderson2021hybrid]
 - Main changes:

@@

::: {.column width="45%"}
::: {.fragment .fade-in fragment-index=2}
 1. Platforms set lump-sum fee $F$
:::
::: {.fragment .fade-in fragment-index=3}
 2. Firms decide whether to enter at cost $c + F$
:::
::: {.fragment .fade-in fragment-index=4}
 3. Firms and platform set product prices, consumers buy products
:::
:::

@@

::: {.column width="45%"}
::: {.fragment .fade-in fragment-index=2}
 1. Firms decide whether to invest at cost $c$
:::
::: {.fragment .fade-in fragment-index=3}
 2. Platform entry fees and decisions are negotiated
:::
::: {.fragment .fade-in fragment-index=4}
 3. Firms and platform set product prices, consumers buy products
:::

>>>>

 - Intentionally simple model
 - Most elements borrowed from [@anderson2021hybrid]
 - Main changes:
   - Lump-sum entry fees
   - Entry fees are not set bilaterally (bargaining)

@@

::: {.column width="45%"}
::: {.fragment .fade-in fragment-index=2}
 1. Platforms set lump-sum fee $F$
:::
::: {.fragment .fade-in fragment-index=3}
 2. Firms decide whether to enter at cost $i + F$
:::
::: {.fragment .fade-in fragment-index=4}
 3. Firms and platform set product prices, consumers buy products
:::
:::

@@

::: {.column width="45%"}
::: {.fragment .fade-in fragment-index=2}
 1. Firms decide whether to invest at cost $i$
:::
::: {.fragment .fade-in fragment-index=3}
 2. Platform entry fees and decisions are negotiated
:::
::: {.fragment .fade-in fragment-index=4}
 3. Firms and platform set product prices, consumers buy products
:::
